miniKanren with fair search strategies

### 2019-05-02 Paper/paper.tex
sort is a tricky word because it has math meanings, use a more specified descriptor, like letter abcd, instead.

\section{introduction}
\NOTE[MVC]{We need clear definitions of the following: fair, almost-fair, and unfair. Either use bullet points, or definition environment. Google ``latex math definition.''}
\NOTE[MVC]{A quick intro to miniKanren would be nice here.}

@@

In the following program, the three \conde clauses differ in a trivial way. So 
we expect lists of each sort constitute $1/4$ of the answer list. However, 
DFS$_\textrm{i}$, the current search strategy, gives us much more lists of \texttt{a} than 
other sorts of lists. And some sorts (e.g. lists of \texttt{c}) are rarely 
found. The situation would be worse if we add more \conde clauses.

@@

In the following program, the three \conde clauses differ in a trivial way. So 
we expect lists of each sort constitute $1/4$ of the answer list. However, 
search strategies with unfair \conj{} (e.g. DFS$_\textrm{i}$, DFS$_\textrm{f}$) give us much 
more lists of \texttt{a} than other sorts of lists. And some sorts (e.g. lists 
of \texttt{c}) are rarely found. Although DFS$_\textrm{i}$'s \disj{} is unfair in general, 
it is fair when there is no call to relational definition in sub-goals, 
including this case. The situation would be worse if we add more \conde 
clauses. The result with DFS$_\textrm{bi}$, whose \conj{} is also unfair, is similar, but 
due to its different \disj{}, the position of \texttt{b} and \texttt{c} are 
swapped.

@@

Intuitively, search strategies with fair \conj{} should produce each sort of 
lists equally frequently. Indeed, BFS does so.

>>>>

\section{introduction}
\NOTE[MVC]{We need clear definitions of the following: fair, almost-fair, and unfair. Either use bullet points, or definition environment. Google ``latex math definition.''}
\NOTE[MVC]{A quick intro to miniKanren would be nice here. We should mention The Reasoned Schemer, 2nd and say DFSi is used there.}

@@

In the following program, the three \conde clauses differ in a trivial way. So 
we expect lists of each letter constitute $1/4$ of the answer list. However, 
DFS$_\textrm{i}$, the current search strategy, gives us much more lists of \texttt{a}s than 
lists of other letters. And some letters (e.g. lists of \texttt{c}) are rarely 
found. The situation would be worse if we add more \conde clauses.

@@

In the following program, the three \conde clauses differ in a trivial way. So 
we expect lists of each letter constitute $1/4$ of the answer list. However, 
search strategies with unfair \conj{} (e.g. DFS$_\textrm{i}$, DFS$_\textrm{f}$) give us much 
more lists of \texttt{a}s than lists of other letters. And some letters (e.g. lists 
of \texttt{c}) are rarely found. Although DFS$_\textrm{i}$'s \disj{} is unfair in general, 
it is fair when there is no call to relational definition in sub-goals, 
including this case. The situation would be worse if we add more \conde 
clauses. The result with DFS$_\textrm{bi}$, whose \conj{} is also unfair, is similar, but 
due to its different \disj{}, the position of \texttt{b} and \texttt{c} are 
swapped.

@@

Intuitively, search strategies with fair \conj{} should produce each letter of 
lists equally frequently. Indeed, BFS does so.
